EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
Edits edits edits

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
and existing open-source test suites were used as baseline. This paper
describes the results obtained by the \EVOSUITE test generation
tool~\cite{FrA11c} in this competition. Details about the procedure of
the competition, the technical framework, and the benchmark classes
can be found in~\cite{sbst17competition}.  In this competition,
\EVOSUITE achieved a 1457.3 overall score, which was the highest among
the competing and baseline tools.

@@

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Techniques such as
\textit{partial minimisation} to only select a few test cases to be
minimised, rather than all test cases; or
\textit{delta-debugging}~\cite{zellerdd}, which could isolate the
relevant statements of each test case, might be worth investigating
to alleviate this issue.

% Mocking
As mentioned in the previous section, \EVOSUITE now uses private
API access and functional mocking%  in addition to environment
% mocking
~\cite{ICST_Mocking17}. In the competition, a total of 20,921
objects were mocked, 1,485 private fields were set and 3,090 private methods
were invoked using mocked access% , and environment classes were
% mocked 4,699 times, with \texttt{java.util.Random} and
% \texttt{java.io.File} being by far the most frequently mocked
% environment classes (resp. 1,286 and 1,121 times)
, adding up to represent only 1.09\% of the total number of lines of code
in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
investigation is needed to assess the impact of these mocking features
on test generation effectiveness for the benchmarks in the
competition.

>>>>

%------------------------------------------------------------------------- 
\section{Introduction}
The annual unit test generation competition aims to drive and evaluate
progress on unit test generation tools. In the 5th instance of the
competition at the International Workshop on Search-Based Software
Testing (SBST) 2017, two tools, \EVOSUITE and \JTEXPERT, competed on a
set of 69 open-source Java classes. Two other tools, \RANDOOP and \TT,
and existing open-source test suites were used as baseline. This paper
describes the results obtained by the \EVOSUITE test generation
tool~\cite{FrA11c} in this competition. Details about the procedure of
the competition, the technical framework, and the benchmark classes
can be found in~\cite{sbst17competition}.  In this competition,
\EVOSUITE achieved an overall score of 1457.3, which was the highest
among the competing and baseline tools.

@@

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Techniques such as
\textit{partial minimisation} to only select a few test cases to be
minimised, rather than all test cases, or more efficient minimisation
based on \textit{delta-debugging}~\cite{LOZCM07}, might be worth
investigating to alleviate this issue.

% Mocking
As mentioned in the previous section, \EVOSUITE now uses private
API access and functional mocking%  in addition to environment
% mocking
~\cite{ICST_Mocking17}. In the competition, a total of 20,921
objects were mocked, 1,485 private fields were set and 3,090 private methods
were invoked using mocked access% , and environment classes were
% mocked 4,699 times, with \texttt{java.util.Random} and
% \texttt{java.io.File} being by far the most frequently mocked
% environment classes (resp. 1,286 and 1,121 times)
, adding up to represent only 1.09\% of the total number of lines of
code in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
investigation would be needed to assess the impact of these mocking
features on test generation effectiveness for the benchmarks in the
competition.
